%\documentclass[12pt,draftcls]{ucdavisthesis}
\documentclass[12pt]{ucdavisthesis}

% PLEASE READ THE MANUAL - ucdavisthesis.pdf (in the package installation directory)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                      %
%               LATEX COMMANDS FOR DOCUMENT SETUP                      %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\usepackage{bookmark}
\usepackage[us,nodayofweek,12hr]{datetime}
\usepackage{graphicx}
%\usepackage[square,comma,numbers,sort&compress]{natbib}
%\usepackage{hypernat}
% Other useful packages to try
\usepackage{bm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{accents}
\usepackage[]{algorithm2e}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    citecolor=black,
    bookmarks=true,
}
\usepackage[raggedright]{titlesec}
\usepackage{gensymb}
%
% Different fonts to try (uncomment only fontenc and one font at a time)
% (you may need to install these first)
%\usepackage[T1]{fontenc} %enable fontenc package if using one of the fonts below
%\usepackage[adobe-utopia]{mathdesign}
%\usepackage{tgschola}
%\usepackage{tgbonum}
%\usepackage{tgpagella}
%\usepackage{tgtermes}
%\usepackage{fourier}
%\usepackage{fouriernc}
%\usepackage{kmath,kerkis}
%\usepackage{kpfonts}
%\usepackage[urw-garamond]{mathdesign}
%\usepackage[bitstream-charter]{mathdesign}
%\usepackage[sc]{mathpazo}
%\usepackage{mathptmx}
%\usepackage[varg]{txfonts}

\hyphenation{dis-ser-ta-tion blue-print man-u-script pre-par-ing} %add hyphenation rules for words TeX doesn't know


%\renewcommand{\rightmark}{\scriptsize A University of California Davis\ldots \hfill Rev.~\#1.0 \quad Compiled: \currenttime, \today}
% a fancier running header that can be used with draftcls options

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                      %
%        DOCUMENT SETUP AND INFORMATION FOR PRELIMINARY PAGES          %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title          {\textsc{Partitioned Polytopal Finite-Element Methods\\
                 for Nonlinear Solid Mechanics}}
%Exact title of your thesis. Indicate italics where necessary by underlining or using italics. Please capitalize the first letter of each word that would normally be capitalized in a title.

\author         {Brian Doran Giffin}
%Your full name as it appears on University records. Do not use initials.

%\authordegrees  {B.S. (University of California, Davis) 2013 \\
%                 M.S. (University of California, Davis) 2014}
                 
%Indicate your previous degrees conferred.

\officialmajor  {\textsc{Civil and Environmental Engineering}}
%This is your official major as it appears on your University records.

\graduateprogram{Civil and Environmental Engineering}
%This is your official graduate program name. Used for UMI abstract.

\degreeyear     {2018}
% Indicate the year in which your degree will be officially conferred.

\degreemonth    {June}
% Indicate the month in which your degree will be officially conferred. Used for UMI abstract.

\committee{\textsc{Mark M. Rashid, Chair}}{\textsc{N. Sukumar}}{\textsc{Boris Jeremi\'{c}}}{}{}
% These are your committee members. The command accepts up to five committee members so be sure to have five sets of braces, even if there are empties.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\copyrightyear{2020}
%\nocopyright

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\dedication{\textsl{To Lyle \ldots \\
            for teaching me how to think deeply, to analyze new information objectively, and to appreciate the complexity and nuanced beauty in all things.} \\
            \textsl{And to Nancy \ldots \\
            for inspiring me to explore my creativity, for giving me canvases to paint on, and the confidence to paint, without fear of failure.}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\abstract{This work presents a novel polytopal finite-element framework that addresses the collective issues of discretization sensitivity and mesh generation for computational solid mechanics problems. The use of arbitrary polygonal and polyhedral shapes in place of canonical isoparametric elements seeks to remediate issues pertaining to meshing and mesh quality (particularly for irregularly shaped elements), while maintaining many of the desirable features of a traditional finite element method.
	
	A general class of \textit{partitioned element methods} (PEM) is proposed and analyzed, constituting a family of approaches for constructing piecewise polynomial approximations to harmonic shape functions on arbitrary polytopes. Such methods require a geometric partition of each element, and under certain conditions will directly yield integration consistency. Two partitioned element methods are explored in detail, including a novel approach herein referred to as the \textit{discontinuous Galerkin partitioned-element method} (DG-PEM). An implementational framework for the DG-PEM is presented, along with a discussion of its associated numerical challenges.
	
	The numerical precision of the PEM is explored via classical patch tests and single element tests for a representative sampling of polygonal element shapes. Solution sensitivity with respect to element shape is examined for a handful of problems, including a mesh convergence study in the nearly incompressible regime. Finally, the efficacy of the DG-PEM is assessed for a number of benchmark problems involving large deformations and nonlinear material behavior.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\acknowledgments{I would like to express my gratitude to the following individuals, without whom this work would not have been possible: Professor Amit Kanvinde, who inspired me to pursue postgraduate study at UC Davis; Professor Sukumar, who first enticed me into exploring the field of computational mechanics; Dr. Joseph Bishop, for being actively involved in my early (and continuing) professional development; Professor Mark Rashid -- my advisor, who turned my initial spark of interest in computational mechanics into a roaring fire of passion; Drs. Steven Wopschall and Omar Hafez, for being my mentors and co-navigators throughout my journey in graduate school; Messrs. Subhajit Banerjee and Eric Chin, whose fruitful discussions helped me to develop a sense of calm and confidence prior to my qualifying examination; Professors Yannis Dafalias, John Bolander, and Elbridge Puckett, whose enthusiasm as lecturers and courtesy as QE examiners were indispensable; Professor Boris Jeremi\'{c}, whose comments have helped to improve upon the organization of this dissertation; Drs. Joseph Jung, Kendall Pearson, Nathan Crane, Michael Tupek, Mr. Mark Merewether, and the whole of the Sierra Solid Mechanics Team at Sandia National Laboratories, who introduced me to the practical aspects of code development; Mses. Carly Arthur, Aim\'{e}e Sylvia, and Mr. Sam Mish, whose conversations as fellow class-mates and advisees were both insightful and inspiring; and foremost to Ms. Maha Kenawy, who has served as my primary role-model and source of inspiration for completing this dissertation. Thank you, all.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Each chapter can be in its own file for easier editing and brought in with the \include command.
% Then use the \includeonly command to speed compilation when working on a particular chapter.
%%% \includeonly{ucdavisthesis_example_Chap1}

\begin{document}

\newcommand{\bibfont}{\singlespacing}
% need this command to keep single spacing in the bibliography when using natbib

\bibliographystyle{plain}
%many other bibliography styles are available (IEEEtran, mla, etc.). Use one appropriate for your field.

\makeintropages %Processes/produces the preliminary pages

\include{introduction}
%\include{mathematics}
\include{solid_mechanics}
%\include{solution_inaccuracy}
\include{pem_formulation}
\include{implementation}
\include{results}
\include{future_work}

\appendix

\include{appendix}

\bibliography{bibliography}

%% The UMI abstract uses square brackets!
%\UMIabstract[This work presents a novel polytopal finite-element framework that addresses the collective issues of discretization sensitivity and mesh generation for computational solid mechanics problems. The use of arbitrary polygonal and polyhedral shapes in place of canonical isoparametric elements seeks to remediate issues pertaining to meshing and mesh quality (particularly for irregularly shaped elements), while maintaining many of the desirable features of a traditional finite element method.
%	
%	A general class of \textit{partitioned element methods} (PEM) is proposed and analyzed, constituting a family of approaches for constructing piecewise polynomial approximations to harmonic shape functions on arbitrary polytopes. Such methods require a geometric partition of each element, and under certain conditions will directly yield integration consistency. Two partitioned element methods are explored in detail, including a novel approach herein referred to as the \textit{discontinuous Galerkin partitioned-element method} (DG-PEM). An implementational framework for the DG-PEM is presented, along with a discussion of its associated numerical challenges.
%	
%	The numerical precision of the PEM is explored via classical patch tests and single element tests for a representative sampling of polygonal element shapes. Solution sensitivity with respect to element shape is examined for a handful of problems, including a mesh convergence study in the nearly incompressible regime. Finally, the efficacy of the DG-PEM is assessed for a number of benchmark problems involving large deformations and nonlinear material behavior.]

\end{document} 
